---
title: "Viz"
author: "Ye Dam Yi"
date: "4/12/2021"
output: html_document
---
```{r libraries}
require(tidyverse)
require(haven)

```


```{r read-data}
risk_all <- read_spss("/Users/yedam/Documents/GitHub/DSP/Project/project7-emotion-risk/data/risk_excluded.sav")
risk_sur <- read_spss("/Users/yedam/Documents/GitHub/DSP/Project/project7-emotion-risk/data/risk_sur.sav")
risk_pred <- read_spss("/Users/yedam/Documents/GitHub/DSP/Project/project7-emotion-risk/data/risk_pred.sav")

write_sav(risk_all, "data/risk_all.sav")
write_sav(risk_sur, "data/risk_sur.sav")
write_sav(risk_pred, "data/risk_pred.sav")


risk_all <- risk_all %>% 
  mutate(gender = as_factor(gender),
         condition = as_factor(condition),
         rel_self = as_factor(rel_self),
         rel_friend1 = as_factor(rel_friend1),
         rel_friend2 = as_factor(rel_friend2)) 

```



```{r theme}

mytheme = theme(
  axis.title.x = element_text(size = 22),
  axis.text.x = element_text(size = 20),
  axis.title.y = element_text(size = 22),
  axis.ticks.length=unit(.25, "cm"),
  axis.text = element_text(size = 18)
)

```

```{r manipulation, fig.height=2, fig.width=3}
jpeg("manipulationcheck.jpg", width = 500, height = 380)

risk_all %>% 
  pivot_longer(c(riskyrisk, riskavrisk), names_to = "option", values_to = "riskrating") %>%  
  ggplot(aes(x = option, y = riskrating, fill = option)) +
  geom_bar(stat = "identity", color = "grey") +
  labs(x = "",
       y = "Risk Levels") +
  scale_x_discrete(labels = c("Stay with Friends", "Approach Barista")) +
  scale_y_continuous(limits = c(1, 5)) +
  theme_classic() +
  mytheme


dev.off()



```

Problem: Error in pivot_longer(., c(riskyrisk, riskavrisk), names_to = "option",  : 
  object 'risk_all' not found
Calls: <Anonymous> ... withVisible -> eval -> eval -> %>% -> ggplot -> pivot_longer
Execution halted

Solution: If you have added eval = FALSE the earlier R code won't execute in which you have created your object. So when you again use that object in a different chunk it will fail with object not found message.

```{r risklevel}
jpeg("risklevel.jpg", width = 500, height = 380)

risk_all %>% 
  group_by(condition) %>% 
  mutate(mean = mean(risklevel),
         sd = sd(risklevel)) %>% 
  ggplot(aes(y = risklevel, x = condition)) +
  geom_boxplot() +
  labs(x = "",
       y = "Risk-Taking Level") +
  geom_errorbar(aes(ymin = risklevel - sd, ymax = risklevel +sd)) +
  scale_x_discrete(labels = c("Self", "Surrogate", "Prediction")) +
  theme_classic() +
  mytheme
dev.off()

```


```{r neg}
jpeg("neg.jpg", width = 500, height = 380)

risk_all %>% 
  ggplot(aes(y = neg, x = condition)) +
  geom_boxplot() +
  labs(x = "",
       y = "Negative Emotion") +
  scale_x_discrete(labels = c("Self", "Surrogate", "Prediction")) +
  theme_classic() +
  mytheme
dev.off()

```


```{r pos}
jpeg("pos.jpg", width = 500, height = 380)

risk_all %>% 
  ggplot(aes(y = neg, x = condition)) +
  geom_boxplot() +
  labs(x = "",
       y = "Positive Emotion") +
  scale_x_discrete(labels = c("Self", "Surrogate", "Prediction")) +
  theme_classic() +
  mytheme
dev.off()

```

```{r alert}
jpeg("alert.jpg", width = 500, height = 380)

risk_all %>% 
  ggplot(aes(y = alert, x = condition)) +
  geom_boxplot() +
  labs(x = "",
       y = "Alertness") +
  scale_x_discrete(labels = c("Self", "Surrogate", "Prediction")) +
  theme_classic() +
  mytheme
dev.off()

```